{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-06-18 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

            The gradient mapping in this case is: 
                \mathcal G_{L_f}x = L_f(x - \Pi_{X}x). 

@@

                Then $f \in \mathbb S(L_f, \kappa_f, X)$ is strongly convex iff 

@@

@@

                    Denoted by $\mathbb S'(L_f, \kappa_f, X)$. 

@@

                    Denoted by $\mathbb U(L_f, \kappa_f, X)$. 

@@

                    Denoted by $\mathbb G(L_f, \kappa_f, X)$. 

@@

                    Denoted by $\mathbb F(L_f, \kappa_f, X)$. 

@@

                    Denoted by $\mathbb E(L_f, \kappa_f, X)$. 

@@

                    \mathbb S'(L_f, \kappa_f, X) \subseteq \mathbb U(L_f, \kappa_f, X). 

@@

@@

                They are labeled for ease of refernecing. 

@@

                    \item The inequality \eqref{ineq:thm:qscnvx-means-qua-proof-item1}. 
                    \item By the property of projection, it has $\Pi_{X^+} x_\tau = \bar x$. 
                    \item The inductive hypothesis with $k \ge 0$. 
                    \item $\bar x = \Pi_{X^+}x$, $X^+$ is the set of minimizer of the of $f$ over $X$, hence $f(\bar x) = f^+$, the minimum. 

@@

                    &\underset{\text{(i)}}{\ge }

@@

                    &\underset{\text{(iii)}}{\ge }

@@

                    &\underset{\text{(ii)}}{=} 

@@

                    &\underset{\text{(iv)}}{=} 

@@

                    \mathbb G(L_f, \kappa_f, X)\subseteq \mathbb U(L_f, \kappa_f, X). 

@@

                    \mathbb S'(L_f, \kappa_f, X) \subseteq \mathbb G(L_f, \kappa_f, X). 

@@

                If $f \in \mathbb S'(L_f, \kappa_f, X)$ then Theorem \ref{thm:qscnvx-means-qua} has $f \in \mathbb U(L_f, \kappa_f, X)$. 

@@

                This is Theorem 2 in the Necoara et al. \cite{necoara_linear_2019}, right after it claims $\mathbb U(L_f, \kappa_f, X)\subseteq \mathbb G(L_f, \kappa_f/2, X)$ under convexity. 

@@

                $x^+$ has descent lemma hence we have 
                    f^+ - f(X) \le f(x^+) - f(x) 
                    \le - \frac{L_f}{2}(1 - \beta)^2 \Vert x - \Pi_{X^+}\Vert^2. 
            Before we start, we will specialize Theorem \ref{thm:cnvx-pg-ineq} because it will be used in later proofs. 

@@

@@

                Let $f$ satisfies Assumtion \ref{ass:necoara-2019-settings}. 
                Suppose that $f \in \mathbb F(L_f, \mu_f, X)$ so it satisfies the quadratic function growth condition. 

@@

                definte projections onto the set of minimizers $x^+_\Pi = \Pi_{X^+} x^+, X_\Pi = \Pi_{X^+}x$, then

@@

                    \right)\Vert x^+ - x_\Pi^+\Vert

@@

                Using convexity, consider \eqref{ineq:proj-grad} with $z = x^+_\Pi$ it yields: 

@@

                    f(x^+) - f(x^+_\Pi) - L_f\langle x_\Pi^+ - x^+, x^+ - x\rangle
                    - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert^2
                    \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2
                    - \Vert L_f(x - x^+)\Vert\Vert x^+_\Pi - x^+\Vert

@@

                    &= \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2

@@

                        + L_f\Vert L_f(x - x^+)\Vert\Vert x_\Pi^+ - x^+\Vert
                    \frac{\kappa_f + L_f}{2}\Vert x^+ - x^+_\Pi\Vert^2

@@

                        \Vert L_f(x - x^+)\Vert + L_f\Vert x - x_\Pi^+\Vert

@@

                From the last line, it's can be equivalently expressed as:

@@

                    \Vert L_f(x - x^+)\Vert + L_f\Vert x^+ - x_\Pi^+\Vert
                    - \sqrt{L_f(\kappa_f + L_f)}\Vert x^+ - x^+_\Pi\Vert

@@

                    - \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - x^+_\Pi\Vert.

@@

                    \mathbb E(L_f, \kappa_f, X) &\subseteq \mathbb F(L_f, \kappa^2_f/L_f, X), 
                    \mathbb F(L_f, \kappa_f) 

@@

                    \mathbb E\left(

@@

@@

                For any $x \in X$, define the gradient projection steps by $x^+ = \Pi_{X}(x - L^{-1}_f\nabla f(x))$. 
                Denote $x^+_\Pi = \Pi_{X^+}x^+$. 
                Let $x_\Pi = \Pi_{X^+}x$, using the property of projection onto $X$ we have 

@@

                    \Vert x - x_\Pi\Vert &\le \Vert x - x_\Pi^+\Vert
                    \le \Vert x - x^+\Vert + \Vert x^+ - x^+_\Pi\Vert

@@

                    &= \frac{1}{L_f}\Vert L_f(x - x^+)\Vert + \Vert x^+ - x^+_\Pi\Vert

@@

                    \Vert x^+ - x^+_\Pi\Vert &\ge
                    \Vert x - x_\Pi\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert. 

@@

                Before we start, we list intermediate results and conditions which are going to be used in the proof that follows for the ease of referencing. 
                    \item The inequality \eqref{ineq:thm:qfg-peb-equiv-proof-item1}. It uses the property of projection onto a set hence convexity of $X^+$ is not needed. 
                Starting with Lemma \ref{lemma:grad-map-qfg} because $f$ satisfies quadratic growth and it is assumed convex, then it has: 

@@

                    - \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - x^+_\Pi\Vert

@@

                    \Vert \mathcal G_{L_f}x\Vert. 

@@

                Skipping some algebra, the fraction simplifies to 
                    \frac{\kappa_f/L_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}. 
                This gives PEB condition. 

@@

                    \mathbb S(\kappa_f, L_f, X) 
                    \subseteq \mathbb S'(\kappa_f, L_f, X)
                    \subseteq \mathbb G(\kappa_f, L_f, X) 
                    \subseteq \mathbb U(\kappa_f, L_f, X) 
                    \subseteq \mathbb F(\kappa_f, L_f, X). 

@@

                $\mathbb S' \subseteq \mathbb G$ is proved in Theorem \ref{thm:qscnvx-implies-qgg} and $\mathbb G \subseteq \mathbb U$ is proved in \ref{thm:qgg-implies-qua}. 
                $\mathbb S\subseteq \mathbb S'$ is obvious and it remains to show $\mathbb U \subseteq \mathbb F$. 
                Let $f\in \mathbb U(\kappa_f, L_f, X)$, it has for all $x \in X$: 

@@

            Necoara re-introduce the bound, the following theorem phrase that upper bound in the exact same way, but with only the Euclidean norm. 

@@

            The following theorem stated their use of the Error bound condition to capture a class of Q-SCNVX function. 

@@

                Then $f(x):= g(Ax)$ is Q-SCNVX with $L_f = L_g\Vert A\Vert^2$, $\kappa_f = \sigma_g/\theta(A, C)^2$. 

@@

                $X\neq \emptyset$ determines a non-empty set of minimizers $X^+ := \argmin_{x \in X} f(x)$. 

@@

                    \item [(b)] There exists uniquely $(t^*, T^*) \in \RR^{m\times n}$ such that for all $\bar x \in X^+$ it has $Ax^+ = t^*, \nabla f(\bar x) = T^*$. In other word, for all minimizers $\bar x$ in $X^+$, $A\bar x$ and, $\nabla f(\bar x)$ are all the same. It would mean $X^+ = \{\bar x : A\bar x = t^*, Cx^* \le d\}$ and, it's also a polyhedron. 

@@

                        \dist(x | X^+) \le \theta(A, C)\dist((Ax - t^*, Cx - d) | \{\mathbf 0\}\times \RR^n_-)

@@

                For all $x \in \RR^n$ denote $\bar x = \Pi_{X^+} x$, using strong convexity of $g$, and $f(x) = g(Ax)$: 

@@

                The set $X^+$ is a convex and, $f$ takes the same value all over it. 

@@

                    &\underset{\text{(c)}}{\ge} \frac{\sqrt{L(\mu + L)} - L}{\sqrt{L(\mu + L)}} \frac{1}{\sqrt{2L}}\left\Vert

@@

                    &= \frac{1}{\sqrt{2L}}\left(

@@

                    &\underset{\text{(d)}}{\ge} \frac{\mu}{2\sqrt{L}}\left(

@@

                    \kappa\left(
                        \frac{\sqrt{L}\left(2 - \sqrt{2}\right)}{4}

@@

                \item [(a)] For the first equality, we assumed that $G^{(J)} < \epsilon$ in the outer loop and, it's returned by Algorithm \ref{alg:xxapg} at line 5. Therefore, it has $G_0 = G^{(J)} = \sqrt{L^{(J)}_0} \Vert z^{(J)} - x_0^{(J)}\Vert$ because it calls Algorithm \ref{alg:armijo-ls} (Armijo line search) with $\alpha_0 = 0$. The second equality comes by using Definition \ref{def:gm-for-ch2}. 

@@

                \item [(d)] The function $x \mapsto 1 - (1 + x/L)^{-1/2}$ is concave hence for all $x \in [0, L]$ it has: 
                    1 - (1 + \mu/L)^{-1/2} &= \left[x \mapsto 1 - (1 + x/L)^{-1/2}\right](0(1 - \mu) + \mu)
                    &\ge 0(1 - \mu) + \mu(1 - 2^{-1/2}) 

@@

                \frac{4e\sqrt{2}(F(z_0) - F^+)^{1/2}}{\kappa\sqrt{L}(2 - \sqrt{2})} 

@@

                    \frac{4e\sqrt{2}(F(z_0) - F^+)^{1/2}}{\kappa \sqrt{L}(2 - \sqrt{2})\delta}

@@

            On a calculator it has $4e\sqrt{2}/(2 - \sqrt{2}) \le 27$ and, $1/(16\sqrt{2 + 2e}) \ge 0.02$ so 
                \Vert z_J - z_J^+\Vert &\le \frac{27(F(z_0) - F^+)^{1/2}}{\kappa}\exp\left(
                    - \frac{K\sqrt{\kappa}}{20}

>>>>

            We define the gradient mapping as: 
                \mathcal G_{L_f}(x) := L_f(x - \Pi_{X}(x - L^{-1}_f \nabla f(x))). 

@@

                Then $f$ is $\kappa_f$ strongly convex and $L_f$ smooth if

@@

                We denote it by $f \in \mathcal S(L_f, \kappa_f, X)$. 

@@

                    Denoted by $\QSCNVX(L_f, \kappa_f, X)$. 

@@

                    Denoted by $\QUA(L_f, \kappa_f, X)$. 

@@

                    Denoted by $\QGG(L_f, \kappa_f, X)$. 

@@

                    Denoted by $\QFG(L_f, \kappa_f, X)$. 

@@

                    Denoted by $\PEB (L_f, \kappa_f, X)$. 

@@

                    \QSCNVX(L_f, \kappa_f, X) \subseteq \QUA (L_f, \kappa_f, X). 

@@

                \begin{align}\label{ineq:thm:qscnvx-means-qua-proof-ih}

@@

                They are labeled for ease of referencing. 

@@

                    \item[(a)] The inequality \eqref{ineq:thm:qscnvx-means-qua-proof-item1} we just showed. 
                    \item[(b)] By the property of projection, it has $\Pi_{X^+} x_\tau = \bar x$. 
                    \item[(c)] The inductive hypothesis, inequality \eqref{ineq:thm:qscnvx-means-qua-proof-ih}. 
                    \item[(d)] $\bar x = \Pi_{X^+}x$, $X^+$ is the set of minimizer of the of $f$ over $X$, hence $f(\bar x) = f^+$, the minimum. 

@@

                    &\underset{\text{(a)}}{\ge }

@@

                    &\underset{\text{(c)}}{\ge }

@@

@@

                    &\underset{\text{(d)}}{=} 

@@

                    \QGG(L_f, \kappa_f, X)\subseteq \QUA(L_f, \kappa_f, X). 

@@

                    \QSCNVX(L_f, \kappa_f, X) \subseteq \QGG (L_f, \kappa_f, X). 

@@

                If $f \in \QSCNVX (L_f, \kappa_f, X)$ then Theorem \ref{thm:qscnvx-means-qua} has $f \in \QUA(L_f, \kappa_f, X)$. 

@@

                This is Theorem 2 in the Necoara et al. \cite{necoara_linear_2019}, right after it claims $\QUA (L_f, \kappa_f, X)\subseteq \QGG (L_f, \kappa_f/2, X)$ under convexity. 

@@

            Prior to proving more theorems, we will specialize Theorem \ref{thm:cnvx-pg-ineq} because it will be used in later proofs. 

@@

                The first inequality is the property of projection onto a set. 
                Now, use \eqref{ineq:proj-grad2}. 
                    f(x^+) - f(x) 
                    \le - \frac{L_f}{2}(1 - \beta)^2 \Vert x - \Pi_{X^+}x\Vert^2. 
                Take the careful observation that inequality \eqref{ineq:proj-grad2} doesn't still hold for weakly convex function. 

@@

                Suppose that $f \in \QFG(L_f, \mu_f, X)$ so, it satisfies the quadratic function growth condition. 

@@

                define projections onto the set of minimizers $\bar x^+ = \Pi_{X^+} x^+, \bar x = \Pi_{X^+}x$, then

@@

                    \right)\Vert x^+ - \bar x^+\Vert

@@

                Using convexity, consider projected gradient inequality \eqref{ineq:proj-grad} with $z = \bar x^+$ it yields: 

@@

                    f(x^+) - f(\bar x^+) - L_f\langle \bar x^+ - x^+, x^+ - x\rangle

@@

                    &\underset{\text{(a)}}\ge
                    \frac{\kappa_f}{2}\Vert x^+ - \bar x^+\Vert^2
                    - \Vert L_f(x - x^+)\Vert\Vert \bar x^+ - x^+\Vert
                    &= \frac{\kappa_f}{2}\Vert x^+ - \bar x^+\Vert^2

@@

                        + 2L_f\Vert L_f(x - x^+)\Vert\Vert \bar x^+ - x^+\Vert
                    &= \frac{\kappa_f + L_f}{2}\Vert x^+ - \bar x^+\Vert^2

@@

                        + 2L_f\Vert L_f(x - x^+)\Vert\Vert \bar x^+ - x^+\Vert
                        + L_f^2\Vert\bar x^+ - x^+\Vert^2
                    \frac{\kappa_f + L_f}{2}\Vert x^+ - \bar x^+\Vert^2
                        \Vert L_f(x - x^+)\Vert + L_f\Vert x - \bar x^+\Vert

@@

                At label (a), we statement hypothesis $f \in \QFG (L_f, \kappa_f, X)$ and, Cauchy inequality. 
                From the last line, it can be equivalently expressed as:

@@

                    \Vert L_f(x - x^+)\Vert + L_f\Vert x^+ - \bar x^+\Vert
                    - \sqrt{L_f(\kappa_f + L_f)}\Vert x^+ - \bar x^+\Vert

@@

                    - \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - \bar x^+\Vert.

@@

                    \QFG (L_f, \kappa_f) 

@@

                    \PEB\left(

@@

                    \right), 
                    \PEB (L_f, \kappa_f, X) &\subseteq \QFG(L_f, \kappa^2_f/L_f, X). 

@@

                For any $x \in X$, define the projected gradient: $x^+ = \Pi_{X}(x - L^{-1}_f\nabla f(x))$. 
                Denote $\bar x^+ = \Pi_{X^+}x^+$. 
                Let $\bar x = \Pi_{X^+}x$, using the property of projection onto $X$ we have 

@@

                    \Vert x - \bar x\Vert &\le \Vert x - \bar x^+\Vert
                    \le \Vert x - x^+\Vert + \Vert x^+ - \bar x^+\Vert

@@

                    &= \frac{1}{L_f}\Vert L_f(x - x^+)\Vert + \Vert x^+ - \bar x^+\Vert

@@

                    \Vert x^+ - \bar x^+\Vert &\ge
                    \Vert x - \bar x\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert. 

@@

                Starting with Lemma \ref{lemma:grad-map-qfg} because $f$ satisfies quadratic growth and, it is assumed convex, then it has: 

@@

                    - \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - \bar x^+\Vert

@@

                    L_f^{-1} \Vert \mathcal G_{L_f}x\Vert. 

@@

                At the label (a), we used inequality \eqref{ineq:thm:qfg-peb-equiv-proof-item1}.
                Continuing with some algebra, we have: 
                    &= \frac{L_f(\kappa_f + L_f) - L_f^2}{\sqrt{L_f(\kappa_f + L_f)}(\sqrt{L_f(\kappa_f + L_f)} + L_f)}
                    &= \frac{L_f \kappa_f}{L_f(\kappa_f + L_f) + L_f\sqrt{L_f(\kappa_f + L_f)}}
                    &= \frac{\kappa_f/L_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}. 
                This gives PEB condition: 
                    \Vert \mathcal G_{L_f}(x)\Vert \ge L_f 
                    \frac{\kappa_f/L_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}\Vert x - \bar x\Vert
                    \frac{\kappa_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}\Vert x - \bar x\Vert. 

@@

                    \mathcal S(\kappa_f, L_f, X) 
                    \subseteq \QSCNVX(\kappa_f, L_f, X)
                    \subseteq \QGG(\kappa_f, L_f, X) 
                    \subseteq \QUA(\kappa_f, L_f, X) 
                    \subseteq \QFG(\kappa_f, L_f, X). 

@@

                $\QSCNVX \subseteq \QGG$ is proved in Theorem \ref{thm:qscnvx-implies-qgg} and $\QGG \subseteq \QUA$ is proved in Theorem \ref{thm:qgg-implies-qua}. 
                $\mathcal S\subseteq \QSCNVX'$ is obvious. 
                It remains to show $\QUA \subseteq \QFG$. 
                Let $f\in \QUA(\kappa_f, L_f, X)$, it has for all $x \in X$: 

@@

            Necoara re-introduce the bound, the following theorem phrase that upper bound in the exact same way, but only with the Euclidean norm. 

@@

            The following theorem stated their use of the this error bound to capture a class of Q-SCNVX function. 

@@

                Define $f(x):= g(Ax)$, then $f$ is Q-SCNVX with $L_f = L_g\Vert A\Vert^2$, $\kappa_f = \sigma_g/\theta(A, C)^2$. 

@@

                $X\neq \emptyset$ gives a non-empty set of minimizers $X^+ := \argmin_{x \in X} f(x)$. 

@@

                    \item [(b)] There exists uniquely $(t^*, T^*) \in \RR^{m\times n}$ such that for all $\bar x \in X^+$ it has $A\bar x = t^*, \nabla f(\bar x) = T^*$. In other word, for all minimizers $\bar x$ in $X^+$, $A\bar x$ and, $\nabla f(\bar x)$ are all the same. It would mean $X^+ = \{\bar x : A\bar x = t^*, C\bar x \le d\}$ and, it's also a polyhedron. 

@@

                        \dist(x |\; X^+) \le \theta(A, C)\dist((Ax - t^*, Cx - d) |\; \{\mathbf 0\}\times \RR^n_-)
                    And for any feasible solution $x \in X$, it simplifies to $\dist(x | X^+) \le \theta(A, C) \dist(Ax - t^* |\; \{\mathbf 0\}\times \RR^n_-)$. 

@@

                For all $x \in X$ denote $\bar x = \Pi_{X^+} x$, using strong convexity of $g$, and $f(x) = g(Ax)$: 

@@

                The set $X^+$ is convex and, $f$ takes the same value all over it. 

@@

                    &\underset{\text{(c)}}{\ge} \frac{L(\sqrt{L(\mu + L)} - L)}{\sqrt{L(\mu + L)}} \frac{1}{\sqrt{2L}}\left\Vert

@@

                    &= \frac{\sqrt{L}}{\sqrt{2}}\left(

@@

                    &\underset{\text{(d)}}{\ge} \frac{\mu\sqrt{L}}{\sqrt{2}}\left(

@@

                    \frac{\kappa}{\sqrt{L}}\left(
                        \frac{\sqrt{2} - 1}{2}

@@

                \item [(a)] For the first equality, we assumed that $G^{(J)} < \epsilon$ in the outer loop and, it's returned by Algorithm \ref{alg:xxapg} at line 5. Therefore, it has $G_0 = G^{(J)} = \sqrt{L^{(J)}_0} \left\Vert z^{(J)} - x_0^{(J)}\right\Vert$ because it calls Algorithm \ref{alg:armijo-ls} (Armijo line search) with $\alpha_0 = 0$. The second equality comes by using Definition \ref{def:gm-for-ch2}. 

@@

                \item [(d)] Define function $h = x \mapsto 1 - (1 + x/L)^{-1/2}$ is concave hence for all $x \in [0, L]$ it has: 
                    1 - (1 + \mu/L)^{-1/2} &= h(0(1 - \mu) + \mu L)
                    &\ge 0(1 - \mu) + \mu\left(1 - (1 + 1)^{-1/2}\right) 

@@

                \frac{2e\sqrt{2L}(F(z_0) - F^+)^{1/2}}{\kappa(\sqrt{2} - 1)} 

@@

                    \frac{2e\sqrt{2L}(F(z_0) - F^+)^{1/2}}{\kappa(\sqrt{2} - 1)\delta} 

@@

            On a calculator it has $(2e\sqrt{2})/(\sqrt{2} - 1) < 19$ and, $1/(16\sqrt{2 + 2e}) > 0.025$ so 
                \Vert z_J - z_J^+\Vert &\le \frac{19\sqrt{L}(F(z_0) - F^+)^{1/2}}{\kappa}\exp\left(
                    - \frac{K\sqrt{\kappa}}{40}
